---
title: "data"
date: last-modified
format:
  html:
    code-fold: true
    code-tools: true
    toc: true
params:
  update_data: true
  update_figs: true
  interest_survey_results_fn: "Quarto workshop Summer 2024 (Responses)"
  csv_dir: data/csv
---

## About

This page has code, images, and data visualizations that support the workshop.

To reveal or hide the code, click on the button at the upper right.

::: {.callout-tip}

Code hiding (folding) and showing is controlled by the `code-fold` and `code-tools` parameters in the YAML header for your document.

:::

## Initial interest survey data

### Download

We download the data as a CSV (if `params$update_data == TRUE`).

```{r set-up-update-data}
if (!dir.exists(params$csv_dir)) {
  message("Creating missing '", params$csv_dir, "'.")
  dir.create(params$csv_dir)
}

if (params$update_data) {
  options(gargle_oauth_email = Sys.getenv("GMAIL_SURVEY"))
  googledrive::drive_auth()
  
  new_fn <- file.path(params$csv_dir, "interest-survey-data.csv")
  if (file.exists(new_fn)) {
    old_fn <- file.path(params$csv_dir, "_interest-survey-data.csv")
    message("File '", new_fn, "' exists: Copying old to '", old_fn, "'.")
    file.rename(new_fn, old_fn)
  }
  
  googledrive::drive_download(
    params$interest_survey_results_fn,
    path = new_fn,
    type = "csv",
    overwrite = TRUE
  )
  message("Data updated.")
} else {
  if (!file.exists(new_fn)) {
    message("File not found: '", new_fn, "': Creating new file.")
  }
}
```
We load the saved CSV.

```{r load-registration-data}
if (params$update_figs) {
  interest <-
    readr::read_csv(new_fn, show_col_types = FALSE)
}
```

### Clean

Generate the beginnings of a data dictionary.

```{r}
interest_qs <- names(interest)
interest_dd <- tibble::tibble(question = interest_qs)

interest_dd <- interest_dd |>
  dplyr::mutate(question_short = c("Timestamp",
                                   "Email",
                                   "Interested",
                                   "Mos",
                                   "Mon_times",
                                   "Tue_times",
                                   "Wed_times",
                                   "Thu_times",
                                   "Fri_times",
                                   "Comments"),
                question_description = c("Submission time",
                                         "Respondent email",
                                         "Interested or not",
                                         "Which month(s) are preferred",
                                         "Morning or afternoon on Monday",
                                         "Morning or afternoon on Tuesday",
                                         "Morning or afternoon on Wednesday",
                                         "Morning or afternoon on Thursday",
                                         "Morning or afternoon on Friday",
                                         "Respondent comments"))
```

#### Process the response data.

Rename the variables using the short names.

```{r}
names(interest) <- interest_dd$question_short
```

Process the 'Mos' variable.

```{r}
interest <- interest |>
  dplyr::mutate(June = stringr::str_detect(Mos, "June"),
         July = stringr::str_detect(Mos, "July"))
```

Process the time of day variables.

```{r}
interest <- interest |>
  dplyr::mutate(Mon_am = stringr::str_detect(Mon_times, "Morning"),
         Mon_pm = stringr::str_detect(Mon_times, "Afternoon")) |>
  
  dplyr::mutate(Tue_am = stringr::str_detect(Tue_times, "Morning"),
         Tue_pm = stringr::str_detect(Tue_times, "Afternoon")) |>

  dplyr::mutate(Wed_am = stringr::str_detect(Wed_times, "Morning"),
         Wed_pm = stringr::str_detect(Wed_times, "Afternoon")) |>
  
  dplyr::mutate(Thu_am = stringr::str_detect(Thu_times, "Morning"),
         Thu_pm = stringr::str_detect(Thu_times, "Afternoon")) |>

  dplyr::mutate(Fri_am = stringr::str_detect(Fri_times, "Morning"),
         Fri_pm = stringr::str_detect(Fri_times, "Afternoon"))
```

### Visualize

```{r}
xtabs(formula = ~ Interested, data = interest)
```

```{r}
#| label: "Which-months"
xtabs(formula = ~ Interested + June, data = interest)
xtabs(formula = ~ Interested + July, data = interest)
```

```{r}
#| label: "Monday-interest"
xtabs(formula = ~ Interested + Mon_am, data = interest)
xtabs(formula = ~ Interested + Mon_pm, data = interest)
```

```{r}
#| label: "Tuesday-interest"
xtabs(formula = ~ Interested + Tue_am, data = interest)
xtabs(formula = ~ Interested + Tue_pm, data = interest)
```

```{r}
#| label: "Wednesday-interest"
xtabs(formula = ~ Interested + Wed_am, data = interest)
xtabs(formula = ~ Interested + Wed_pm, data = interest)
```

```{r}
#| label: "Thursday-interest"
xtabs(formula = ~ Interested + Thu_am, data = interest)
xtabs(formula = ~ Interested + Thu_pm, data = interest)
```

```{r}
#| label: "Friday-interest"
xtabs(formula = ~ Interested + Fri_am, data = interest)
xtabs(formula = ~ Interested + Fri_pm, data = interest)
```

As of `{r} Sys.time()`, Thursday afternoon seems like the most popular time.
